Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-07 paper/paper.tex
paper.tex

\begin{figure}[]
    {\footnotesize\input{pictures/top_optimization}}
    \caption{
        Genetic optimization process of genotypes with Erdös-Renyi topology
        ($N=100$ fixed) for the challenges $C\ix{high}$ and $C\ix{low}$.
        In each figure, one can see the $50$ genotypes of every Generation
        (single dots) together with the respective mean values (thick
        lines). Figures (a) to (c) depict the evolution of the three
        parameters ($\gain$, $\feedback$, and $\ERprob$) being optimized,
        while figure (d) shows the development of the fitness values.
    }
    \label{fig:freq_optimization}
\end{figure}

@@

Nevertheless *ABSCHLUSSSATZ*

>>>>

\begin{figure}[]
    {\footnotesize\input{pictures/top_optimization}}
    \caption{
        Genetic optimization of genotypes with an fraction $q$ of Erdös-Renyi
        topology and $1-q$ of ring topology for the challenge $C\ix{high}$.
        This figure is to be understood like FIG. \ref{fig:freq_optimization}.
    }
    \label{fig:top_optimization}
\end{figure}

@@

Nevertheless we were able to produce successful optimization results
and could indeed show that adaption to high frequencies can not only be
accomplished by an implausible effect, namely the 
high feedback values, but also by changing the topological structure of the
network. In this regard it would certainly be interesting to further
inquire, how genotypes that allow for a more fine grained control over the
topology behave under the optimization.
